\documentclass[12pt,notitlepage]{report}
\input{setup/mainsetup}
\input{setup/specifics}

\usepackage{comment}
%\excludecomment{proof}

\addbibresource{refs.bib}

\title{Reconstruction of Lorentzian manifolds from null cone light observation sets}
\author{Alexander Uhlmann\thanks{auhlmann@ethz.ch}\\
Advisor: Prof. Dr. Peter Hintz}

\begin{document}
\maketitle


\begin{abstract}
    Let $(M,g)$ be a globally hyperbolic Lorentzian manifold and $p^+\gg p^-$ be points in $M$ separated by a timelike curve. Let $V$ be an open subset of $\jp = J^+(p^-)\cap J^-(p^+)$. We show that the topological, differentiable and conformal structure of $V$ can be uniquely reconstructed from the \emph{light observation sets} on the future null boundary $K$ of $\jp$, i.e. the sets $\mc{P}_K(q) \coloneqq  \mc{L}^+_q \cap K$ for $q\in V$. Furthermore we show that we can reconstruct the topological data of $V$ also if it extends to include the boundary $K$, even though the light observation sets are degenerate in this case.
    % ((TODO: 
    % --do more with conclusion chapter 
    % --finish $dH\to0$ on bounday proof 
    % --fix $g\rvert_K$ situation and $\Theta$ construction & show constr of \Theta from data
    % -- DirReconstr continuous 
    % +use coloneqq for definitions 5min
    % +clean up appendices 30min
    % +explain plots more 15min
    % +explain end of ch4 1h
    % +do short minkowski case exmaple in introduction 30min
    % -do declaration of originality 10min
    % +finalize title 10min
    % +do aknowledgemets 20min
    % +fix all other (()) 15min
    % clean up bibliography 10min
    % ==3h
    % ))
\end{abstract}

\chapter*{Acknowledgments}
I am immensely grateful to my advisor Prof. Hintz for his support throughout this thesis. I really appreciated the weekly meetings and his infectious enthusiasm. Without him this thesis would not have been possible. 

I would also like to express my gratitude to my partner who was always there for me and made the last year the wonderful moment it was.

I am also deeply grateful my parents for their unconditional support, whatever I have been doing.

And finally I would like to thank my friends, who helped make my studies the interesting and joyous time they were.

\tableofcontents

%\newpage

\include{01-intro}
\include{02-machinery}
\include{03-interior}
\include{04-boundary}
%\include{04-intro}
\include{D-applications}
\include{05-discussion}


%\include{05-reconstruction}
%\include{06-applications}
%\include{07-boundary}

%\include{02-causality}
%\include{03-reconstruction}

\newpage

\nocite{*}
\printbibliography

\appendix

\include{A1-technicalities}
\include{A2-causality}
\include{A3-relativity}

%\include{01-notes}

%\includepdf[pages={-}]{declaration-originality.pdf}

\end{document}